Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-02-21 ms.tex
Filling in BH demo section

The existence of a minimum heating rate for thermal stability (eq.~[\ref{eq:cooling2}]) implies a corresponding maximum accretion rate,
\begin{align}
\frac{\dot{M}_{\rm TI}}{\dot{M}_{\rm edd}} \simeq
  {\rm min}\begin{cases}
   4\times 10^{-4} \eta_{0.02}^{0.47} M_{\bullet,8}^{0.34} &, \text{core}\\
   2\times 10^{-4} \eta_{0.02}^{0.59} M_{\bullet,8}^{0.29}    &, \text{cusp}\\
\eta M_{\bullet}/\dot{M}_{\rm edd}t_{\rm h} \approx 5.5\times 10^{-5}\eta_{0.02}&, v_{\rm TI} < \sigma,
  \end{cases}
  \label{eq:Mdotmax}
\end{align}
which is derived using equation (\ref{eq:eddr_analytic}) to calculate $\dot{M}(v_{\rm TI})$.

@@

{\bf BDM: ADD plot of parameter space of MBH and stellar age, showing Ia heating versus stellar heating; thermally stable versus unstable regions ($t_{\rm ff} = t_{\rm cool}/10$); as well as where $\sigma = v_{w}^{\bullet}$ and $\sigma = v_{w}^{\star}$.  }

>>>>

The existence of a minimum heating rate for thermal stability (eq.~[\ref{eq:cooling2}]) implies a corresponding maximum accretion rate,
\begin{align}
\frac{\dot{M}_{\rm TI}}{\dot{M}_{\rm edd}} \simeq
  {\rm min}\begin{cases}
   4\times 10^{-4} \eta_{0.02}^{0.47} M_{\bullet,8}^{0.34} &, \text{core}\\
   2\times 10^{-4} \eta_{0.02}^{0.59} M_{\bullet,8}^{0.29}    &, \text{cusp}\\
\eta M_{\bullet}/\dot{M}_{\rm edd}t_{\rm h} \approx 6. 6\times 10^{-5}\eta_{0.02}&, v_{\rm TI} < \sigma,
  \end{cases}
  \label{eq:Mdotmax}
\end{align}
which is derived using equation (\ref{eq:eddr_analytic}) to calculate $\dot{M}(v_{\rm TI})$.

@@

There is a maximum accretion rate for a thermally stable flow
(eqn. [\ref{eq:Mdotmax}]). This gives a lower bound on the growth
time from thermally stable accretion

\begin{align}
  t_{\rm growth}/t_{\rm h} \gsim
  \rm{max}\begin{cases}
    9 \eta_{0.02}^{-0.47} \Mbh^{-0.34} &, \text{core}\\
    15 \eta_{0.02}^{-0.59} \Mbh^{-0.29} &, \text{cusp}\\
    50  \eta_{0.02}^{-1} &, v_{\rm TI} < \sigma
  \end{cases}
  \label{eq:tgrow_min}
\end{align}

In Figure~\ref{fig:bh_growth} we plot the growth times for core and
cusp galaxies, with parameters chosen for the average star formation
history at each $\Mbh$ (see Figure~\ref{fig:vwSources}
and~\ref{fig:eta}). Core and cusp galaxies are shown in green and blue
respectively.  We also plot the maximum growth time for thermal
instability from equation~\eqref{eq:tgrow_min} in purple.

\begin{figure}
\includegraphics[width=\columnwidth]{bh_growth.eps}
\caption{\label{fig:bh_growth} Growth times $\Mdot/\MdotEdd$ in units
  of the Hubble time $\th$ for core ($\Gamma=0.1$, blue) and cusp
  ($\Gamma=0.8$, green). These are calculated from
  equation~\ref{eq:tgrow_analytic} with parameters chosen for the
  average star formation history at each $\Mbh$. We also plot a lower
  bound on growth time for a themally stable flow (purple) from
  equation~\eqref{eq:tgrow_min}.}
\end{figure}
